Plant-pollintor networks worldwide are composed by the same specific building

### 2021-06-08 Draft/Draft.Rmd
Nacho's edits on Intro and MM. Good job!

Ecological processes leave distinct structural imprints on indirect interactions in mutualistic networks. Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors. However, recent work has shown the network meso-scale can capture this important information. The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e. motifs) and those constitute the building blocks of the whole network. Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ... Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif. ... Hence, we show that species ecology is shaping the building blocks that conform the web of life.

@@

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the network structure have proven common invariant structural properties across them including nestedness [@jordano2003], the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009] and a degree distribution that decays as a power law [@jordano2003]. In addition, phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of plant-pollinator interactions and network structure [@stang2006; @peralta2020]. However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].

Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation. Despite their relevance in ecological communities, plant-pollinator research fails to capture indirect interactions with the traditional analytical tools that condense the information in single indices (e.g., netedness or interaction frequency). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore what are the general patterns of indirect interactions in plant-pollinator networks.

Linking the structural porperties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, motifs are abstract representations often decoupled from species ecology. Remarkably, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021]. Further, although some studies have evaluated plant reproductive strategies in plant-pollinator networks [tur2013; @lazaro2020], they are often overlooked [@devaux2014]. Hence, exploring how the main reproductive groups integrate with the emergent motif framework can shed light of key aspects of ecosystem functioning.

Here, we used 60 plant-pollinator networks from 18 different studies and grouped the different plant and pollinator species into functional groups that summarized the main reproductive strategies. Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks. Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour. Then, we explored the frequency of motifs up to five nodes in these set of plant-pollinator networks. Finally, we explore if the different plants and pollinators functional groups are over- or under-represented by comparing their frequencies with simulated networks.

@@

[potential additions: 
Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...
Finally, we draw a network collapsing nodes per FG...]

>>>>

Ecological processes leave distinct structural imprints on species interactions shaping  the topology of mutualistic networks. Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors. However, recent work has shown the network meso-scale can capture this important information. The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e. motifs) and those constitute the building blocks of the whole network. Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ... Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif. ... Hence, we show that species ecology is shaping the building blocks that conform the web of life.

@@

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano2003](idem, aqui molaria citar el original del 98, si no me equivoco), nestedness [@jordano2003](Aqui la cita seria Bascompte PNAS), or the imbalance between plants and pollinators with approximately four times more pollinator species [@vazquez2009](Esta no estoy seguro no sea un artefacto del muestreo... quizas la quitamos? buscamos otra?). In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016, @stang2006; @peralta2020]. However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].

Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@Gazoul200XJEcol?]. Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g. interaction frequency) or in single topological indices (e.g. nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore which are the general patterns observed in the distribution of plant-pollinator motifs worldwide.

Motifs are abstract representations often decoupled from species ecology. Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux201X?]. For example, bees are more specialized foragers [Jose, aquí por ejemplo, pueden decir que abejas pequeñas y generalistas, pueden comportarse muy diferente que grandes y especialistas... si tienes una lista de pollintors, con su familia, pasamela, y le hecho un ojo](), usually alble to open complex zygomorphic flowers which are not accessible to fly pollinators. How this different behaviors translate into their interaction topology is unknown. Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions. Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies. Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.

Here, we used 60 plant-pollinator networks from 18 different studies distributed worldwide, alongside a detailed grouping of plants into reproductive strategies and pollinator species into functional groups. Plants were grouped based on a comprehensive dataset that included floral, reproductive and vegetative traits compiled in Lanuza et al., (unpublished) on a larger set of plant-pollinator networks. Pollinators were grouped into the main taxonomical groups that differed in life form and behaviour. Then, we explored which motifs up to five nodes in these set of plant-pollinator networks were over and under-represented. Finally, we explore if the different plants and pollinators functional groups are over- or under-represented in certain positions.

@@

[potential additions: 
Finally,for each motif, we recover the number of times a given combination of functional groups emerges ...]
